---
title: "Random variables, probabilities and distributions"
output: html_document
date: '2022-07-12'
---

```{r load-libraries, message = F, warning = F}
library(tidyverse)
```



## Notes


### Sample space

The **sample space** is the set of all possible outcomes of an experiment.

#### Discrete examples

- Experiment 1: You flip a coin once. The sample space is $\{H, T\}$.

We separate each outcome by a comma and use brackets $\{ \}$ to denote a "set".

- Experiment 2: You flip a coin twice. The sample space is $\{ HH, HT, TH, TT\}$

- Experiment 3: You roll a die once. The sample space is $\{ 1, 2, 3, 4, 5, 6\}$

- Experiment 4: You send out a survey asking participants whether they prefer cats or dogs. The sample space is $\{ \text{Cats}, \text{Dogs} \}$

- Experiment 5: A car manufacturer makes 100 vehicles. You count the number of recalls. The sample space is $\{1, 2, 3, \ldots, 99, 100 \}$

#### Continuous examples

- Experiment 6: You observe the numeric grade you earn in a course. The sample space is $[0, 100]$

Here we write the lower bound and upper bound of the sample space and assume we can observe all values in-between. Brackets, $[$ $]$, are inclusive of the end values while parentheses, $($ $)$, are not.

- Experiment 7: You measure the tail length of American alligators The sample space is $(0, c ]$ feet where $c$ is the maximum tail length of an alligator, e.g. $c$ might be approximately 10.

- Experiment 8: You measure the geographic coordinates (longitude and latitude) of a COVID case. The sample space is $[-90, 90]$ for latitude and $[-180, 180 ]$ for longitude. 

### Events

An **event** is a collection of 1 or more outcomes.

#### Examples

- You roll a die once. Let *A* be the event that you roll an even number, i.e. *A* $= \{2, 4, 6 \}$

- A car manufacturer makes 100 vehicles. You count the number of recalls. Let *B* be the event you see fewer than 10 recalls. *B* $= \{1, 2, 3, \ldots, 8, 9 \}$

- You observe the numeric grade you earn in a course. Let *C* be the event you receive an **A**. *C* $= [93, 100]$

## Practical answers to easy questions in R

#### 1

You toss a fair coin 10 times. Let *A* be the event there is at least one head.

What is the probability of *A*?

```{r coin-1}

N = 10000
coin_flips = data.frame(num_heads = rbinom(n = N, size = 10, prob = 0.5))

coin_flips %>%
  filter(num_heads >=1) %>%
  nrow() / N

```


#### 2 

You roll a six-sided die 5 times. Let *A* be the event that you roll exactly one two. What is the probability of *A*?

```{r dice-1}
outcomes = 1:6
one.roll = function() {
  roll = sample(outcomes, size = 1, replace = TRUE)
  return(roll)
}

five.rolls = function() {
  rolls = replicate(5, one.roll())
  return(sum(rolls == 2) == 1)
}

samples = replicate(10000, five.rolls())
mean(samples)

```




