---
title: "Schedule"
output:
  html_document:
    css: "./custom-site.css"
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, eval=F)
```

```{r load-libraries}
library(tidyverse)
library(knitr)
```

```{r smart-date-setup}
# set these:
firstDay = as.Date("2022-06-27")
firstDayID = "Mon"
lastDay = as.Date("2022-08-04")
lectureDays = c("Mon", "Tue", "Thu")
labDays = c("Tue", "Thu")
holidays = as.Date(c("2022-07-04"))
### render table
allDates = seq(from = firstDay, to = lastDay, by = 'day')
schedule = data.frame(allDates,
                        dayOfWeek = weekdays(allDates, abbreviate=T)) %>%
  filter(dayOfWeek %in% c(lectureDays, labDays))
schedule = schedule %>%
  mutate(lab = ifelse(dayOfWeek %in% labDays, TRUE, FALSE)) %>%
  mutate(Topic = ifelse(allDates %in% holidays, "NO CLASS", "")) %>%
  mutate(Date = format(allDates, format = "%b %d")) %>%
  mutate(Date = paste(dayOfWeek, Date)) %>%
  mutate(Week = rep("", nrow(schedule))) %>%
  mutate(Prepare = rep("", nrow(schedule))) %>%
  mutate(AE = rep("", nrow(schedule))) %>%
  mutate(Assignment = rep("", nrow(schedule))) %>%
  mutate(Exam = rep("", nrow(schedule))) %>%
  mutate(Project = rep("", nrow(schedule))) %>%
  select(Week, Date, Topic, Prepare, AE, Assignment, Exam, Project)
# to be pasted into console then pasted into markdown:
schedule %>%
  kable(format = "markdown")
```

Summer II, 2022

|Week |Date       |Topic    |Prepare |AE |Lab |Exam |Project |
|:----|:----------|:--------|:-------|:--|:----------|:----|:-------|
|   1  |Mon Jun 27 |  Intro to R       |        |[ae01](/static/static/appex/ae1.html)   |           |     |        |
|  1   |Tue Jun 28 |  Visualization I       |        | | [lab1]()             |     |        |
|  1   |Thu Jun 30 |  Visualization II       |        | | [lab2]()             |     |        |
|  2   |Mon Jul 04 |NO CLASS: Independence Day |        |   |           |     |        |
|  2   |Tue Jul 05 | Simple Linear Regression        |     | | [lab3]()            |     |        |
|  2   |Thu Jul 07 | Multiple linear regression        |        | | No lab: exam01 released           |  [exam01]()   |        |
|  3   |Mon Jul 11 | Multiple linear regression II       |        |   |           |  exam01 due   |        |
|  3   |Tue Jul 12 | Logistic regression         |        | |  Regression project: workday         |     |        |
|  3   |Thu Jul 14 | Random variables       |        | | [lab4]()              |     |        |
|  4   |Mon Jul 18 | Distributions         |        |   |           |     |        |
|  4   |Tue Jul 19 | Simulation-based inference I       |        |  | [lab5]()              |     |        |
|  4   |Thu Jul 21 | Simulation-based inference II         |        | | [Final project: workday]              |     |        |
|  5   |Mon Jul 25 | Hypothesis testing I        |        |   |           |     |        |
|  5   |Tue Jul 26 | Hypothesis testing II        |        | | [lab6]()              |     |        |
|  5   |Thu Jul 28 | Central Limit Theorem (CLT)       |        |  | Final project: peer-review             |     |        |
|  6   |Mon Aug 01 | Regression + inference        |        |   |           |     |        |
|  6   |Tue Aug 02 | Data science ethics        |        | | [lab7]()           |     |        |
|  6   |Thu Aug 04 | Special topic: Cryptanalysis       |        | | Final project: workday             |     |        |